Non-Euclidean space as revealed by proper distances from Mercury to Venus

### 2023-11-28 mercury_and_venus.Rmd
underbrace

$$
\int_{r=w}^{wx}\frac{dr}{\sqrt{1-1/r}}=w(x-1)+\frac{\log(x)}{2} -w^{-1}\frac{3(1-x)}{8x}+{\mathcal O}\left(w^{-2}\right)
$$
(writing $w$ for Mercury's orbital radius).  Noting that $x\sim 1$, the first two terms are about

>>>>

$$
\int_{r=w}^{wx}\frac{dr}{\sqrt{1-1/r}}=\underbrace{w(x-1)}_{\mbox{Euclid}}+\frac{\log(x)}{2} -w^{-1}\frac{3(1-x)}{8x}+{\mathcal O}\left(w^{-2}\right)
$$
(writing $w$ for Mercury's orbital radius).  Noting that $x\sim 1$, the first two terms are about
